Contention management for Cloud RAN over an optical ring

### 2018-07-30 ISCIS/article.tex
papier format conf

%\documentclass[]{algotel}
%\usepackage[utf8]{inputenc}

%\usepackage{xspace}
%\usepackage{graphicx,graphics} 
%\usepackage{mathtools, bm}
%\usepackage{caption}
%\usepackage{amssymb, bm}
%\usepackage{complexity}
%\usepackage{amsthm}
%%\usepackage{authblk}
%\usepackage{color}
%\usepackage{amsmath}
%\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
%\captionsetup{justification=centering,margin=0.5cm}
\documentclass[]{llncs}
%
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{caption}

\usepackage{graphicx}

\newcommand\pall{\textsc{pall}\xspace}
\newcommand{\todo}[1]{{\color{red} TODO: {#1}}}	
\newtheorem{prop}{Proposition}
\renewcommand{\thefootnote}{\*}

\graphicspath{{img/}}
\title{Contention management for Cloud RAN over an optical ring}
\author{Dominique Barth \inst{1}
  \and Ma\"el Guiraud \inst{1}
   \and Yann Strozecki \inst{1}
  }

\institute{David Laboratory, UVSQ}

@@

\begin{abstract}
The N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency$\dots$) without using expensive end to end connections. We study the compatibility of such a technology with the development of the Cloud RAN, a latency critical application which is a major aspect of 5G deployment. We show that deterministically managing Cloud RAN traffic minimizes its latency while also improving the latency of the other traffics. 
\keywords{Optical ring \and Latency \and C-RAN \and SDN}
\end{abstract}

@@

  \begin{figure}[h!]
       \begin{minipage}[b]{0.5\linewidth}
        \begin{center}
      \includegraphics[scale=0.7]{containers}

      \end{center} 
  \end{minipage}
    \begin{minipage}[b]{0.5\linewidth}
        \begin{center}
      \includegraphics[scale=0.7]{containers2}

      \end{center} 
  \end{minipage}

@@

   \vspace{0.5cm}
  \hspace{-0.75cm}
    \begin{minipage}[b]{0.50\linewidth}

@@

     \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}
      \end{center} 
  \end{minipage}
\hfill
  \begin{minipage}[b]{0.40\linewidth}

@@

  \centering
  \begin{tabular}{|c|c|}
  \hline
  Bit rate of an electronic interface $R$ & $10$ Gbps \tabularnewline
  \hline
  Optical ring bit rate $F\times R$ & $100$ Gbps \tabularnewline
  \hline
    Acceleration factor $F$ & $10$  \tabularnewline
  \hline
  Container size  $C$ & $100$ kb  \tabularnewline
  \hline
  Unit of time $C/(F\times R)$ & $1~\mu$s \tabularnewline
  \hline
  Length of the ring $RS$ & $100$ \tabularnewline
  \hline
  Emission time $ET$ & $500$ \tabularnewline
  \hline
   Period $P$ & $1,000$ \tabularnewline
  \hline
  Number of RRH & $5$  \tabularnewline
  \hline
  Number of nodes $n$ & $5$  \tabularnewline
  \hline
   Load induced by C-RAN traffic & $50\%$  \tabularnewline
  \hline
    Load induced by BE traffic & $40\%$  \tabularnewline
  \hline
  \end{tabular}
  }

  \captionof{figure}{Experimental parameters of the N-GREEN architecture}\label{fig:params}

  \end{minipage}

@@

We now present an algorithm to determine an assignment of the $m_i$, using the method of Prop.\ref{prop:assign} to set the offset at the same positions. We propose three variations to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.

@@

      \includegraphics[scale=0.55]{repart0}
     \caption{Packing.}\label{fig:packing}

@@

  \begin{minipage}[b]{0.45\linewidth}
\centering
      \includegraphics[scale=0.25]{repart1res}
     \captionof{figure}{Impact of the repartition on the latency.}   \label{fig:algocmp}
  \end{minipage} 
  \hfill
  \begin{minipage}[b]{0.45\linewidth}
\centering
      \includegraphics[scale=0.25]{optim.pdf}
     \captionof{figure}{Impact of the deterministic method on the traffics.}   \label{fig:optimres}
  \end{minipage}

  The performance of the reservation algorithm is excellent, since the C-RAN traffic has {\bf zero latency} and the BE traffic has a \textbf{better latency} with reservation than with the FIFO rule. It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth for the BE traffic.

>>>>

%\documentclass[]{algotel}
%\usepackage[utf8]{inputenc}
\documentclass[10pt, conference, letterpaper]{IEEEtran}
%
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{caption}
\usepackage{authblk}
\usepackage{graphicx}

\usepackage{xspace}
\usepackage{graphics} 
\usepackage{mathtools, bm}

\usepackage{amssymb, bm}
\usepackage{complexity}
\usepackage{amsmath,amsthm}

\usepackage{color}
\usepackage{amsmath}
%\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
\captionsetup{justification=centering,margin=0.5cm}

\newcommand\pall{\textsc{pall}\xspace}
\newcommand{\todo}[1]{{\color{red} TODO: {#1}}}	
\newtheorem{prop}{Proposition}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]

\renewcommand{\thefootnote}{\*}

\graphicspath{{img/}}
\title{Contention management for Cloud RAN over an optical ring}

\author[1]{Dominique Barth}
\author[1,2]{Ma\"el Guiraud}
\author[1]{Yann Strozecki}
\affil[1]{David Laboratory, UVSQ}
\affil[2]{Nokia Bell Labs France}

@@

\begin{abstract}
The N-GREEN project has for goal to design a low cost optical ring technology with good performances (throughput, latency$\dots$) without using expensive end to end connections. We study the compatibility of such a technology with the development of the Cloud RAN, a latency critical application which is a major aspect of 5G deployment. We show that deterministically managing Cloud RAN traffic minimizes its latency while also improving the latency of the other traffics.

\end{abstract}

@@

  \begin{figure}[h!]

        \begin{center}
      \hspace{-2.3cm}\includegraphics[scale=0.7]{containers}

   \vspace{0.5cm}

      \includegraphics[scale=0.7]{containers2}
      \end{center}

@@

   \vspace{0.5cm}
  \hspace{-0.75cm}

@@

     \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}

@@

  \begin{tabular}{|c|c|}
  \hline
  Bit rate of an electronic interface $R$ & $10$ Gbps \tabularnewline
  \hline
  Optical ring bit rate $F\times R$ & $100$ Gbps \tabularnewline
  \hline
    Acceleration factor $F$ & $10$  \tabularnewline
  \hline
  Container size  $C$ & $100$ kb  \tabularnewline
  \hline
  Unit of time $C/(F\times R)$ & $1~\mu$s \tabularnewline
  \hline
  Length of the ring $RS$ & $100$ \tabularnewline
  \hline
  Emission time $ET$ & $500$ \tabularnewline
  \hline
   Period $P$ & $1,000$ \tabularnewline
  \hline
  Number of RRH & $5$  \tabularnewline
  \hline
  Number of nodes $n$ & $5$  \tabularnewline
  \hline
   Load induced by C-RAN traffic & $50\%$  \tabularnewline
  \hline
    Load induced by BE traffic & $40\%$  \tabularnewline
  \hline
  \end{tabular}
  }

  \captionof{figure}{Experimental parameters of the N-GREEN architecture}\label{fig:params}
      \end{center}

@@

We now present an algorithm using reservation as in Prop.\ref{prop:assign} to set the offsets at the same position.
In the naive version of the algorithm, we put each RRH in an arbitrary position, for instance one RRH by position.
 We then propose three ideas to optimize the latency of the BE traffic, by spacing as well as possible the free containers in a period.

@@

      \includegraphics[scale=0.5]{repart0}
     \caption{Packing.}\label{fig:packing}

@@

\begin{center}
      \includegraphics[scale=0.25]{repart1res}
     \captionof{figure}{Impact of the repartition on the latency.}   \label{fig:algocmp}

\vspace{0.5cm}

      \includegraphics[scale=0.25]{optim.pdf}
     \captionof{figure}{Impact of the deterministic method on the traffics.}   \label{fig:optimres}

\end{center}
  The performance of the reservation algorithm is excellent, since the C-RAN traffic has {\bf zero latency} and the BE traffic has a \textbf{better latency} with reservation than with the FIFO rule. It is due to the balancing of the load of the C-RAN traffic over the period, that guarantee a more regular bandwidth for the BE traffic.
